TSELM: Target speaker extraction using discrete tokens and language models

### 2024-09-06 src/paper.tex
initial version

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction (TSE) aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. Most models nowadays are discriminative models. They 
utilize a masking strategy to minimize the distance between the clean speech and estimated 
speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}. To solve these issues, researchers have proposed generative models. This method aims to learn the underlying distribution of the target speaker's voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather 
than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied. It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.

>>>>

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction (TSE) aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. Most models nowadays are discriminative models. They 
utilize a masking strategy to minimize the distance between the clean speech and estimated 
speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}. 
To solve these issues, researchers have proposed generative models. This method aims to learn the underlying distribution of the target speech and generate it rather
than mapping from mixed speech to clean speech. 
Some generative models, like diffusion
models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied. 
It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.
